---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# likRatioPlot

<!-- badges: start -->
<!-- badges: end -->

The package likRatioPlot provides a function to generate a plot that shows the relationshp between the prior odds, likelihood ratio and posterior odds, with a particular emphasis on the role uncertainty in the prior odds and likelihood ratio plays on uncertainty in the posterior odds.

## Installation

You can install the development version of likRatioPlot from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jrodu/likRatioPlot")
```

## Example

Below is a likelihood ratio plot when the computed point estimate for the likelihood ratio is 10, with an uncertainty interval between 8 and 12, and a prior odds point estimate of .8 with uncertainty interval from .6 to 1.

```{r example}
library(likRatioPlot)

lik_ratio_plot(10, c(8, 12), .8, c(.6, 1))

```

